### 2015-08-11 rscripts/data_review.Rmd
prepping for PCA

>>>>

1. consider subset - subset of records? subset of users?  subset of locations?  want predictions about location "class", so subset of locations?  later, when locations classified, subset of users.
2. using subset and some predictor measurements

```{r,echo=F}
## principle components analysis
predictors <- function(SD) with(SD, {
  duration <- logout - login
  total_login_time <- sum(duration)
  SD[,sum(logout - login), by=weekday]
  list(
    lifetime = max(logout) - min(login),
    ave_duration = mean(duration),
    med_duration = median(duration),
    sd_duration = sd(duration),
    max_duration = max(duration),
    total_user_time = total_login_time
  )
})

censor.dt[,predictors(.SD), by=location_id]
```

* * *
